---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RiskMapNTDtest

<!-- badges: start -->
[![CRAN version](https://www.r-pkg.org/badges/version/RiskMapNTDtest)](https://cran.r-project.org/package=RiskMapNTDtest)
[![R-CMD-check](https://github.com/claudiofronterre/RiskMapNTDtest/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/claudiofronterre/RiskMapNTDtest/actions/workflows/R-CMD-check.yaml)
[![CRAN downloads](https://cranlogs.r-pkg.org/badges/RiskMapNTDtest)](https://cran.r-project.org/package=RiskMapNTDtest)
[![Total downloads](https://cranlogs.r-pkg.org/badges/grand-total/RiskMapNTDtest)](https://cran.r-project.org/package=RiskMapNTDtest)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
<!-- badges: end -->

## Overview

`RiskMapNTDtest` provides tools for model-based geostatistical analysis of continuous,
binomial and Poisson outcomes.

- Fit spatial and spatio-temporal Gaussian process models.
- Generate predictive surfaces and target summaries.
- Run simulation-based diagnostics and validation workflows.

The methodology is described in *Model-based Geostatistics for Global Public
Health* by Diggle and Giorgi.

## Start Here: MBG-R Book

For a full applied guide to using `RiskMapNTDtest` in real public health workflows,
see the online book by **Emanuele Giorgi and Claudio Fronterre**:

**Model-based geostatistics for global public health using R**
<https://www.mbgr.org/>

## Installation

Install the stable version from CRAN:

```{r, eval=FALSE}
install.packages("RiskMapNTDtest")
```

Install the development version from GitHub:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("claudiofronterre/RiskMapNTDtest")
```

## Quickstart

A minimal linear Gaussian geostatistical model of the form
$Y(x) = \beta_0 + S(x)$, where $S(x)$ is a spatial Gaussian process
can be fitted with:

```{r, eval=FALSE}
library(RiskMapNTDtest)

data(italy_sim)

fit <- glgpm(
  formula = y ~ gp(x1, x2),
  data = italy_sim,
  family = "gaussian",
  crs = 32634,
  messages = FALSE
)

summary(fit)
```

## Learn More

- MBG-R book: <https://www.mbgr.org/>
- Package website: <https://claudiofronterre.github.io/RiskMapNTDtest/>
- Issue tracker: <https://github.com/claudiofronterre/RiskMapNTDtest/issues>
